Self-test prime dimensional EPR pairs with constant alphabet

### 2019-01-27 Draft/draft.tex
Honghao: completed self-testing proof, rescaled weighted CHSH test, removed single value test and added equations for the linear system game

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}

@@

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. Many copies of the $2$-dimensional EPR
pair can be self-tested in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but growing answer alphabet.

So far, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}
\label{thm:inf}
	There exists a set $D$ of odd prime numbers such that for any $d \in D$, 
	the maximally entangled state of local dimension $d$ can be self-tested 
	with constant question and answer sets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d$ whose primitive root is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}
\label{thm:pr_2}
	All maximally entangled state with local dimension $d$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
Note that although the sizes of the question and answer
sets do not depend on $d$, the optimal correlation does.
This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the game we designed consists of several sub-tests, we introduce the individual
sub-tests and their implications in \cref{sec:comp}. Our main result is based the combination
of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
our nonlocal game to self-test maximally entangled state of different dimensions.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.

\textbf{The EPR pair.} Our goal is to self-test maximally entangled state of local dimension $d$, 
\begin{align}
\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
\end{align}
The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
which have operators of the similar form
\begin{align}
	X = \sum_{i=0}^{d-1} \omega_d^i\ketbra{i}{i} && U = \sum_{i=0}^{d-1} \ketbra{i/2}{i},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $i$ is taken modulo $d$.
for example, the $i/2$ above.

@@

	for some $\alpha$, then

@@

After proving the robust the self-testing result, we take one step further and observe some interesting behaviour of the 

@@

	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_B(\ketbra{\tpsi}{\tpsi}))$ such that 

@@

\textbf{Nonlocal game}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give ananswer for a chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new nonlocal game.

@@

The main contribution of our work is the construction of a nonlocal game $\G{d}$ with constant-sized $X$,$Y$,$A$ and $B$
that can be used to self-test $\ket{\EPR{d}}$ for arbitrary odd prime $d$. 
The nonlocal game is a linear system game with modifications or further enforcements. 
We introduce the definition of self-testing first and then the definition of linear system game, 
which come from Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
 and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
 \begin{align*}
 	a(y) &= b && \text{(Consistency)} \\
	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
 \end{align*}
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
\label{sec:comp}
%========================================
The goal of this section and the next section is to 
present a nonlocal game that can self-test $\ket{\EPR{d}}$, 
where $d$ is prime and has primitive root $2$\footnote{By $d$ has primitive root $2$,
we mean that $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.}
The game we constructed is denoted by $\G{d}$, which is the combination of several tasks.
In this section, we introduce such tests and their implications.
In \cref{sec:main}, we show how the implications can be combined to give a full self-test of $\ket{\EPR{d}}$. 
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
is included in the group $K$.
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}

\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game, $\LS$, over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$
into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}..
\begin{proof}
The first step is to embed $\Pg$ into a linear-plus-conjugacy group $\Pg''$ where
all the generators are of order $2$, following the instructions given in the proof of  
Proposition~$4.8$ of the Ref.~\cite{slofstra2017}.
We first introduce $x_1,x_2$ such that $x_1^2=x_2^2=e$, $x=x_1x_2$ and $u x_2 u^{-1}=x_2$.
We also introduce $x' = ux_1u^{-1}$, 
then we embed $\Pg$ in $\Pg'$ as
\begin{align}
	\Pg' = \langle x_1,x_2,x',u: x_1^2=x_2^2=x'^2=e,
	x_1x_2x_1=x', ux_1u^{-1}=x', ux_2u^{-1} =x_2 \rangle.
\end{align}
Next, we introduce $u_1,u_2$ such that $u_1^2=u_2^2=e$ and $u=u_1u_2$, 
and also $u_3.u_4$ of order $2$ such that the conjugacy relations involving them are 
\begin{align*}
u_2x_2u_2 = u_3, && u_1u_3u_1 = x_2\\
u_2x_1u_2 = u_4, && u_1u_4u_1 = x',
\end{align*}
then
$\Pg'$ is further embedded in $\Pg''$ as
\begin{equation}
\begin{aligned}
	\Pg'' =  \langle &x_1,x_2,x',u_1,u_2,u_3,u_4: \text{all elements are of order $2$},\notag\\
	 &u_2x_2u_2 = u_3, u_1u_3u_1 = x_2,
u_2x_1u_2 = u_4, u_1u_4u_1 = x',x_1x_2x_1=x' \rangle.
\end{aligned}
\end{equation}	
To represent the conjugacy relations by a tuple, we relabel the some of the generators as
\begin{align*}
	u_1 = x_3, && u_2 = x_4, && x' = x_5, && u_3 = x_6, && u_4 = x_7,
\end{align*}
so that a simpler form of the group $\Pg''$ is 
\begin{equation}
\begin{aligned}
	\Pg'' = \langle \{x_i\}_{i=1}^7 : x_i^2 = e \; \forall i, 
	x_1x_2x_1=x_5, x_4x_2x_4 = x_6,
	 x_4x_1x_4=x_7, x_3x_2x_3 = x_6, x_3x_5x_3=x_7\rangle
\end{aligned}
\end{equation}
We collect the subscript of $x_i$'s in the conjugacy relations and define
\begin{align}
	C= \{ &(1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
\end{align}
so that $(i,j,k) \in C$ if and only if $x_ix_jx_i = x_k$ in $\Pg''$.

@@

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\end{proof}
%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $U$ by
$\CHSH_U$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}

@@

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but growing answer alphabet.

In summary, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $d-1$ can be self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$ by explicitly giving the 
correlation that achieves this goal. Then the self-testing property of this correlation is 
given in the following theorem.
\begin{theorem}
\label{thm:pr_2}
	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
	primitive root $2$, can be self-tested by a constant-sized correlation.
\end{theorem}
Note that although the sizes of the question and answer
sets do not depend on $d$, the optimal correlation does.
This correlation can be easily converted to work for dimensions with primitive $3$ or $5$.

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is decomposed into two binary observables, which is not done before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the game we designed consists of two sub-tests, we introduce one test
in \cref{sec:lsg} and one in \cref{sec:chsh}. Our main result is based the combination
of the sub-tests and presented in \cref{sec:main}. In \cref{sec:extend}, we show how to adapt
our nonlocal game to self-test maximally entangled state of different dimensions.

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
We use $[n]$ to denote the set $\{0,1 \dots n-1\}$ and $[n]+1$ for the set $\{1,2 \dots n\}$.
%We denote the group commutator of $A$ and $B$, i.e. $ABA^{-1}B^{-1}$, by $[A,B]$.
The EPR pair of local dimension $d$ for $d \geq 2$ is the maximally entangled state and is denoted by
\begin{align}
\ket{\EPR{d}} = \frac{1}{\sqrt{d}} \sum_{i = 0}^{d-1} \ket{ii}.
\end{align}
The superscript $(d)$ stresses the local dimension and we follow this convention through this paper.

We self-test $\ket{\EPR{d}}$ by verify that Alice and Bob has operators 
which have operators of the similar form
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/2}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$th root of unity.
Through out this paper, any operation on the label of the eigenvector $k$ is taken modulo $d$,
unless otherwise specified, for example, the $i/2$ above.

@@

	for some $\epsilon$, then

@@

After proving the robust self-testing result, we take one step further and observe an interesting property of the 

@@

	maximal value of $\I_{\cot(-\pi/2d)} $ implies that there exist states $\ket{u_0}, \ket{u_1} \in \supp(\Tr_A(\ketbra{\tpsi}{\tpsi}))$ such that 

@@

\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new nonlocal game.

@@

The main contribution of our work is the construction of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that its optimal correlation can self-test $\ket{\EPR{d}}$ for arbitrary $d \in D$. 
The nonlocal game is a linear system game with modifications and strict enforcements. 
We introduce the definition of self-testing first and then the definition of linear system game, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a nonlocal game self-tests a quantum state $\ket{\Psi}$ if 
	any quantum strategy $S$ that achieves the optimal quantum value uses a shared state equivalent up to local isometry to $\ket{\Psi}$.
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = b$ be an $m \times n$ linear system over $\Z_2$. The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $1 \leq x \leq m$ and replies with $a \in \Z_2^{\times n}$,
 and Bob is given a variable number $y$ and replies with an assignment $b \in \Z_2$. The winning condition is 
 \begin{align*}
 	a(y) &= b && \text{(Consistency)} \\
	\sum_{y = 1}^n H_{xy} a(y) &\equiv b(x) \pmod 2. &&\text{(Constraint satisfaction)}
 \end{align*}
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.

%The main tool to understand linear system game is through its solution group over $\Z_d$.
%\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
%	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
%	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
%	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
%	\begin{align}
%		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
%	\end{align}
%	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
%	\begin{align}
%		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
%	\end{align}
%	Then the solution group has presentation 
%	\begin{align}
%	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
%	\end{align}
%\end{definition}
%Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
%Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
%\begin{definition}[Operator solution]
%	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
%	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
%	representation mapping $\J$ to $\overline{\omega_d}\1$.
%\end{definition}
%What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
%linear system game from its operator solution and vice versa.

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $2$. 
If $d$ has primitive root $2$,
then $2$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$.
When $d$ is prime, $\Z_d^\times = \{1,2\dots d-1\}$.
The correlation we constructed is the optimal correlation for a game $\G$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$, which
is included in the group $K$, which has presentation
\begin{align*}
	K = \langle a,b,c,x,y: a^2=b^2=c^2 = e, c=ab, yay^{-1} = a, yby^{-1}= c, xyx^{-1} = y^2\rangle.
\end{align*}
The main component of $\G$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg= \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}

\begin{proposition}
	\label{prop:embed}
	The group $\Pg$ can be embedded into a linear system game, $\LS$, over $\Z_2$,
	with $118$ variables and $91$ equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg$
into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Slofstra's seminal work \cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}..
\begin{proof}
The first step is to embed $\Pg$ into a linear-plus-conjugacy group $\Pg''$ where
all the generators are of order $2$, following the instructions given in the proof of  
Proposition~$4.8$ of the Ref.~\cite{slofstra2017}.
We first introduce $x_1,x_2$ such that $x_1^2=x_2^2=e$, $x=x_1x_2$ and $u x_2 u^{-1}=x_2$.
We also introduce $x' = ux_1u^{-1}$, 
then we embed $\Pg$ in $\Pg'$ as
\begin{align}
	\Pg' = \langle x_1,x_2,x',u: x_1^2=x_2^2=x'^2=e,
	x_1x_2x_1=x', ux_1u^{-1}=x', ux_2u^{-1} =x_2 \rangle.
\end{align}
Next, we introduce $u_1,u_2$ such that $u_1^2=u_2^2=e$ and $u=u_1u_2$, 
and also $u_3.u_4$ of order $2$ such that the conjugacy relations involving them are 
\begin{align*}
u_2x_2u_2 = u_3, && u_1u_3u_1 = x_2\\
u_2x_1u_2 = u_4, && u_1u_4u_1 = x',
\end{align*}
then
$\Pg'$ is further embedded in $\Pg''$ as
\begin{equation}
\begin{aligned}
	\Pg'' =  \langle &x_1,x_2,x',u_1,u_2,u_3,u_4: \text{all elements are of order $2$},\notag\\
	 &u_2x_2u_2 = u_3, u_1u_3u_1 = x_2,
u_2x_1u_2 = u_4, u_1u_4u_1 = x',x_1x_2x_1=x' \rangle.
\end{aligned}
\end{equation}	
To represent the conjugacy relations by a tuple, we relabel the some of the generators as
\begin{align*}
	u_1 = x_3, && u_2 = x_4, && x' = x_5, && u_3 = x_6, && u_4 = x_7,
\end{align*}
so that a simpler form of the group $\Pg''$ is 
\begin{equation}
\begin{aligned}
	\Pg'' = \langle \{x_i\}_{i=1}^7 : x_i^2 = e \; \forall i, 
	x_1x_2x_1=x_5, x_4x_2x_4 = x_6,
	 x_4x_1x_4=x_7, x_3x_2x_3 = x_6, x_3x_5x_3=x_7\rangle
\end{aligned}
\end{equation}
We collect the subscript of $x_i$'s in the conjugacy relations and define
\begin{align}
	C= \{ (1,2,5), (3,5,7), (4,1,7), (4,2,6), (3,2,6)\},
\end{align}
so that $(i,j,k) \in C$ if and only if $x_ix_jx_i = x_k$ in $\Pg''$.

@@

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\end{proof}
%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.

%======================================
\section{The extended weighted CHSH game}
\label{sec:chsh}
%======================================
The extended weighted CHSH game is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution have eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$U$ and $X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $U$ by
$\CHSH_U$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
